---
title: "Lab 2 - Linguistic Survey Stat 215A, Fall 2018"
author: "Daniel Soriano"
date: "9/21/2018"
header-includes:
   - \usepackage{float}
output: 
  pdf_document:
    number_sections: true
---

You don't have to slavishly follow this template. Please use this
structure for your report. Your report should be no more than 12 pages, including figures. Indicate your collaborators on the assignment, if you had
any.

```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# load in packages
library(tidyverse)
library(forcats)
library(lubridate)
library(stringr)
library(ggplot2)
library(gridExtra)
library(maps)
library(kableExtra)
library(expss)
library(leaflet)
# load in the loadData() functions
source("R/load.R")
# load in the cleanData() functions
source("R/clean.R")
# load in the plot functions
source("R/plot.R")
```

```{r load-data, echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE}

# load ling data
ling_data <- loadLingData()

# load location data
ling_location <- loadLingLocation()

# load questions and answers data from dialect Survey
load("data/question_data.RData")

# load US state map data
state_df <- map_data("state")

```
# Introduction


# The Data


## Data quality and cleaning

This dataset isn't as bad as the redwood data, but there are still
some issues. You should discuss them here and describe your strategies
for dealing with them.


## Exploratory Data Analysis

This is where you compare pairs of questions with discussion and plots.


# Dimension reduction methods

This is where you discuss and show plots about the results of whatever
dimension reduction techniques you tried - PCA, hierarchical clustering,
K-means, random projections, etc.


# Stability of findings to perturbation


# Conclusion